### 2019-06-08 2-Chapters/2-Chapter/chapter2.tex
Lots of small typos.

More recently, the \klUCB-switch from \cite{Garivier18} is the first algorithm to be proved to
enjoy simultaneously a distribution-free regret bound of optimal order $\sqrt{KT}$, and a distribution-dependent regret bound of optimal order as well, that is, matching the $C_I \ln(T)$ lower bound by \cite{LaiRobbins85}.
It is an index policy that uses a modified version of the indexes of the \klUCB$^+$ algorithm, for arms that are not sampled much, and a modified version of the indexes of the MOSS$^+$ algorithm, for the other arms.
To detail this, first let $f(T, K) = \lfloor (T/K)^{\gamma}\rfloor$ for $\gamma=1/5$,
then \klUCB-switch use the index defined as follows:
%
\begin{align}\label{eq:2:indexes_for_klUCBswitch}
    U^{\mathrm{MOSS}+}_k(t) & \eqdef \frac{X_k(t)}{N_k(t)} + \max\left(0, \sqrt{ \frac{\log\left(\frac{T}{K N_k(t)}\right)}{N_k(t)}} \right). \\
    U^{\KLUCB+}_k(t) & \eqdef \sup\limits_{q \in [a, b]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \frac{\log(\frac{T}{K N_k(t)})}{N_k(t)} \right\} \\
    U^{\klUCB\text{-}\mathrm{switch}}_k(t) & \eqdef \begin{cases}
        U^{\KLUCB+}_k(t) & \text{if } N_k(t) \leq f(T, K), \\
        U^{\mathrm{MOSS}+}_k(t) & \text{if } N_k(t) > f(T, K).
    \end{cases}.
\end{align}

>>>>

More recently, the \klUCB-switch from \cite{Garivier18} is the first algorithm to be proved to
enjoy simultaneously a distribution-free regret bound of optimal order $\sqrt{KT}$, and a distribution-dependent regret bound of optimal order as well, that is, matching the $C_I \ln(T)$ lower bound by \cite{LaiRobbins85}.
It is an index policy that uses a modified version of the indexes of the \klUCB$^+$ algorithm (see \cite{Honda2019} for more details), for arms that are not sampled much, and a modified version of the indexes of the MOSS$^+$ algorithm, for the other arms.
To detail this, first let $f(T, K) = \lfloor (T/K)^{\gamma}\rfloor$ for $\gamma=1/5$,
then \klUCB-switch use the index defined as follows:
%
\begin{align}\label{eq:2:indexes_for_klUCBswitch}
    U^{\mathrm{MOSS}+}_k(t) & \eqdef \frac{X_k(t)}{N_k(t)} + \max\left(0, \sqrt{ \frac{\log\left(\frac{T}{K N_k(t)}\right)}{N_k(t)}} \right). \\
    U^{\KLUCB+}_k(t) & \eqdef \sup\limits_{q \in [a, b]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \frac{\log(\frac{T}{K N_k(t)})}{N_k(t)} \right\} \\
    U^{\klUCB\text{-}\mathrm{switch}}_k(t) & \eqdef \begin{cases}
        U^{\KLUCB+}_k(t) & \text{if } N_k(t) \leq f(T, K), \\
        U^{\mathrm{MOSS}+}_k(t) & \text{if } N_k(t) > f(T, K).
    \end{cases}.
\end{align}
